Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 introduction.tex
Reworded sentence in introduction
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1145 ccdd05d5-56c1-461a-bf98-85f6876523b4

In the era of first-generation detectors, the \GW{} community initiated a
project to send alerts when potential \GW{} transients were observed in order
to trigger followup observations by \EM{} telescopes.  The typical latencies
were 30--60 minutes \citep{HugheyGWPAW2011}, which was an important
achievement, but far too late to catch prompt \EM{} emission. We have the
ambition of reporting \GW{} candidates not minutes \emph{after} the merger, as
has already been accomplished, but seconds \emph{before}.

>>>>

In the first generation of ground-based laser interferometers, the \GW{}
community initiated a
project to send alerts when potential \GW{} transients were observed in order
to trigger followup observations by \EM{} telescopes.  The typical latencies
were 30--60 minutes \citep{HugheyGWPAW2011}, which was an important
achievement, but far too late to catch prompt \EM{} emission. We have the
ambition of reporting \GW{} candidates not minutes \emph{after} the merger, as
has already been accomplished, but seconds \emph{before}.
